\documentclass[11pt]{report}
\usepackage{geometry}
\geometry{left=3cm,right=2.5cm,top=3.5cm,bottom=2.5cm}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Tongwei Zhang}
\chead{40044711}
\lhead{Function Requirements}
\cfoot{\thepage}
\begin{document}
\section*{Requirements Fundamentals}
\subsection*{1 General description of Application}
    ETERNITY:FUNCTIONS is an extension of a typical scientific calculator, each individual needs to complete one of the function that provided by project description. For this part, the \textbf{standard deviation function} needs to be implements, which is calculated by the following Mathematical formula:
    \vspace{0.5cm}
 $$\sigma=\sqrt{\frac{1}{n}{\sum_{i=1}^n(x_i-\bar{x})^2}}$$
The detail requirements are presented in the following subsections.
\subsection*{2 Stakeholders}
The stakeholders of this ETERNITY:FUNCTIONS product is all people who will use this application calculate discreteness of sample data, developer and maintainer.
\subsection*{3 Requirements attributes of F10:$\sigma$}
\textbf{Re.1 \hspace{1cm} priority: 1}\hspace{1cm} Available Functions display
\vspace{0.2cm}\\
When the ETERNITY:FUNCTIONS calculator starts, the console should be able to display the available functions from F1:$arccos(x)$ to F10:$\sigma$.
\vspace{0.2cm}\\
\textbf{Re.2 \hspace{1cm} priority: 1}\hspace{1cm}  Functions selection
\vspace{0.2cm}\\
According to the available functions, user can select the function they want, then enter the parameter input interface.
\vspace{0.2cm}\\
\textbf{Re.3 \hspace{1cm} priority: 1}\hspace{1cm}  Parameter input}
\vspace{0.2cm}\\
The user can enter the parameter according the interface guidelines, the guidelines depends on the specific function that user selected since the needed parameters are different.
\vspace{0.2cm}\\
\textbf{Re.4 \hspace{1cm} priority: 3}\hspace{1cm}  Get the result}
\vspace{0.2cm}\\
After the parameters input, the console can show the result of selected function.
\vspace{0.2cm}\\
\textbf{Re.5 \hspace{1cm} priority: 2}\hspace{1cm}  Whether start another calculate}
\vspace{0.2cm}\\
After get the needed result, the console can provide choices either exit the application or launch another round calculation. 
\vspace{0.2cm}\\
\textbf{Re.6 \hspace{1cm} priority: 2}\hspace{1cm}  Input parameter validation check}
\vspace{0.2cm}\\
In the data input process, the application should be able to check the validation of input parameter and give the corresponding reminder.
\vspace{0.2cm}\\
\textbf{Re.7 \hspace{1cm} priority: 2}\hspace{1cm}  Decimal digits number selection}
\vspace{0.2cm}\\
After input all the sample values, the user can input the number of decimal that they want.
\subsection*{4 ETERNITY:FUNCTIONS constraints}
1. The implements of this scientific calculator cannot use the java internal library suck as Math and so on.\\
2. The result of ETERNITY:FUNCTIONS should be same as the real scientific calculator. 
\end{document}